PACE 2024: OCMu64, reductions and a branch-and-bound solver for\\ One-sided Crossing Minimization

### 2024-09-03 tex/poster.tex
Change Strongly Fixed Pairs paragraph

        \textbf{The lemma is optimal:}
        Suppose that $u, v \in B$ with $N(u) \neq N(v)$ are not strongly fixed, and let $i$ be
        such that $b:=N(u)_i > N(v)_{\lfloor i\cdot m/n\rfloor}=:a$.
        Assuming there exist vertices $m$ in between $a$ and $b$, $l$ left of $\min
        N(v)$ and $r$ right of $\max N(u)$ \ragnar{Is this strong enough? Do $u$ and $v$
          need reversing? Or should we just say left of the min and right of the max
          of the two?}, there exists some \emph{weighted} distribution $X$ over
        $\{l, m, r\}$ such that $c(v, X, u) < \min(c(X, u, v), c(u, v, X))$, so that
        $v$ may have to go before $u$.

@@

      \begin{block}{Practically fixed pairs}
        Although such a function $X$ may exist in theory, it does
        not have to exist in the actual set $B$, motivating a more practical approach:

>>>>

        \textbf{The lemma is optimal:}
        Without further assumptions on $(A, <)$ or on the other elements of $B$, it is not
          possible to prove $u \b v$ if $(u, v)$ is not strongly fixed.
        Suppose that $u, v \in B$ with $N(u) \neq N(v)$ are not strongly fixed, and let $i$ be
        such that $b:=N(u)_i > N(v)_{\lfloor i\cdot m/n\rfloor}=:a$. Now take sets of vertices $L, M,
          R \subseteq A$ with $a < M < b$, with $L < \min(N(v))$ and with $R > \max(N(u))$.
          Add a node $X \in B$ connected to $L, M, R$. With the correct numbers of vertices in
          $L, M, $ we can make it so that $c(v, X, u) < \min(c(X, u, v), c(u, v, X))$, so that
        $v$ has to go before $u$.

@@

      \begin{block}{Practically fixed pairs}
        Although such a node $X$ may exist in theory, it does
        not have to exist in the actual set $B$, motivating a more practical approach:
